\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

The \emph{constraining element} is an intuitive term which indicates the actual type of constraint. For the majority of the constraint types, there is exactly one constraining element. For the constraint type \emph{property domain (R-25, R-26)} which restricts the domain of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}. For a few constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated for these constraint types. The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict given data properties to have a minimum, maximum, or exact number of relationships to literals with certain language tags. Thus, three constraining elements are needed in order to be able to express each possible constraint of that comstraint type.

If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like DL concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$) and (in)equality (=, $\ne$). In case, constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse widely used terms from SPARQL and the DCMI Metadata Terms like \emph{regex} and \emph{xsd:pattern}. For some constraint types like \emph{cardinality restrictions}, it is more intuitive to reuse the DL terms $\geq$ and $\leq$ as constraining elements instead of, for instance, \emph{minimum qualified cardinality restriction}. We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.

>>>>

The \emph{constraining element} is an intuitive term which indicates the actual type of constraint. For the majority of the constraint types, there is exactly one constraining element. For the constraint type \emph{property domain (R-25, R-26)} whose constraints restrict domains of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}. For a few constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated. The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict data properties to have a minimum, maximum, or exact number of relationships to literals with selected language tags. Thus, three constraining elements are needed to express each possible constraint of that constraint type.

If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), equality (=), and inequality ($\ne$). In case constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse terms from SPARQL (e.g., \emph{regex}) and XML Schema constraining facets (e.g., \emph{minInclusive}). For some constraint types like \emph{cardinality restrictions}, it is more intuitive to reuse the DL terms $\geq$ and $\leq$ as constraining elements instead of, for instance, \emph{minimum qualified cardinality restriction}. We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.
